Notice Scripts

### 2018-01-28 Manuscript1.Rmd
Files update

---
title: "Post-Disturbance Diversity Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Department of Ecology, University of Edimburgh
    address: >
      Street address,
      Zip code,
      Country.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal 00679993
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >  # Pour coordonne les packages LateX (supplémentaires)
  \usepackage{amsmath}
bibliography: references.bib # .bib à activer seulement pour git et word format (pandoc fait la biblio)
csl: 
lang: english # french
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook
#   bookdown::pdf_book:
#     base_format: EcoFoG::article
#     keep_tex: TRUE
#  bookdown::word_document2
# output_dir pour articles?
#organiser le code, avec les script et DB adéquats. Mettre un code dans les figures pour indiquer le code d'où elle provient. ../ pour référer à des sous dossiers
---

@@

```{r Options, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning=FALSE, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), out.width = '50%',fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package)}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
source("Scripts/DrawingTools.R")
source("Scripts/GithubPages.R")
```

>>>>

---
title: "Post-Disturbance Diversity Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Department of Ecology, University of Edimburgh
    address: >
      Street address,
      Zip code,
      Country.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal 00679993
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >  # Pour coordonne les packages LateX (supplémentaires)
  \usepackage{amsmath}
bibliography: references.bib # .bib à activer seulement pour git et word format (pandoc fait la biblio)
csl: 
lang: english # french
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook
#   bookdown::pdf_book:
#     base_format: EcoFoG::article
#     keep_tex: TRUE
#  bookdown::word_document2
#Mettre un code dans les figures pour indiquer le code d'où elle provient. ../ pour référer à des sous dossiers
---

@@

```{r Options, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning=FALSE, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), out.width = '40%',fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package)}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
source("Scripts/DrawingTools.R")
source("Scripts/GithubPages.R")
```

### 2018-01-28 Scripts&DB_description.Rmd
Files and html update
Files update

- *TaxoComposition_ForGraphs*: Coordinates of inventories and plots in the 2 dimensions space from taxonomic composition NMDS. 
Lists the coordinates along the various iteration: for now on, only 5 repetitions (becaus run locally).

- *FunctionalComposition_forGraphs*: Coordinates of inventories and plots in the 2 dimensions space from functional composition NMDS. 
Lists the coordinates along the 50 iteration. Comes from the script: *FunctionalNMDS.R*

-*ReplacementTraj_ForGraphs*: List by treatment of plots Richness, Shannon and Simpson diversity along inventoried year. 
It gives the 0.025, 0.5 and 0.975 quantiles from 50 repetitions.
Comes from the script: *ReplacementTraj_ForGraphs.R*

-*FunctionalTraj_ForGraphs*: List by treatment of plots Rao diversity along inventoried year. 
It gives the 0.025, 0.5 and 0.975 quantiles from *only 5 for now* repetitions.

@@

>>>>

- *TaxoComposition_ForGraphs*: Coordinates of inventories and plots in the 2 dimensions space from taxonomic composition NMDS. 
Lists the coordinates along the various iteration: for now on, only 5 repetitions (becaus run locally). **Figure 1 & 2 (a)**.

- *FunctionalComposition_forGraphs*: Coordinates of inventories and plots in the 2 dimensions space from functional composition NMDS. 
Lists the coordinates along the 50 iteration. Comes from the script: *FunctionalNMDS.R*. **Figure 1 & 2 (b)**.

- *ReplacementTraj_ForGraphs*: List by treatment of plots Richness, Shannon and Simpson diversity along inventoried year. 
It gives the 0.025, 0.5 and 0.975 quantiles from 50 repetitions.
Comes from the script: *ReplacementTraj_ForGraphs.R*. **Figure 3**.

- *FunctionalTraj_ForGraphs*: List by treatment of plots Rao diversity along inventoried year. 
It gives the 0.025, 0.5 and 0.975 quantiles from *only 5 for now* repetitions. **Figure 4**.

@@

- *DrawingTools.R*: To alleviate the *Manuscript* file I defined separately the functions to draw the plots from dataset.
